Analysis paper

### 2021-06-15 analysis/analysis.Rmd
update plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)

@@

## Todo

-   [ ] final decision on the Christmas period. Do we want to also exclude target end dates, or just forceast dates? Do we want to exclude the 2nd of January?
-   [ ] look more closely into the stratification: do we want the current thing or do we want something else that has the outcome in it as well? One thing I thought was have another category: inflection or no inflection and also score that?
-   [ ] Talk to Johannes about whether we want to score log forecasts and log truth values instead. I for now removed that part for the following reasons: I currently don't have a good feeling for what it does. I'm somewhat hesitant that establishing a completely new way of scoring forecasts could be beyond the scope of this paper. Very happy to switch to it entirely if we agree it is the better metric, but not sure we are at that point yet.

@@

```{r}
dailytruth_data %>%
  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
                target_end_date <= max(forecast_dates$full_hub_period)) %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_point(size = 0.3) + 
  geom_line(size = 0.5) + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  labs(y = "Observed values", x = "Date") + 
  theme_light()

@@

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df) {
  p <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 1,
                 position = position_dodge(width = 6)) + 
  geom_point(aes(shape = classification)) + 
  geom_line() + 
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

df <- unfiltered_data[model %in% regular_models &
                        quantile %in% c(0.025, 0.25, 0.75, 0.975)] %>%
  dcast(... ~ quantile, value.var = "prediction")
df <- merge(
  df[, c("classification", "speed") := NULL], 
  copy(epitrend)[, forecast_date := NULL], 
  by = c("target_end_date", "location_name", "target_type")
)

@@

for (horizon in 1:4) {
  # plot for cases
  truth_vs_forecast_cases <- df[grepl(horizon, target)] %>%
    dplyr::filter(target_type == "case") %>%
    truth_and_pred_plot() + 
    scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[-2]) + 
    labs(y = "Cases", x = "")

@@

  # plot for deaths
  truth_vs_forecast_deaths <- df[grepl(horizon, target)] %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_pred_plot()  + 
  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "Deaths", x = "")

@@

pairwise <- pairwise_comparison(scores_target_forecastdate, 
                                summarise_by = summarise_by, 
                                baseline = "Baseline")
pairwise <- pairwise[compare_against == "Baseline"]

# create helper function to plot forecasts -------------------------------------
scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = 0,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

# create plots for all horizons ------------------------------------------------
for (i in 1:4) {
  scores_over_time_case <- pairwise[horizon == i & target_type == "case"] %>%
    scores_over_time_plot() + 
    scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[-2]) + 
    labs(y = "WIS rel. to baseline", x = "")

@@

  scores_over_time_deaths <- pairwise[horizon == i & target_type == "death"] %>%
    scores_over_time_plot() + 
    scale_color_brewer(palette = "Accent") + 
    annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
             xmax = max(forecast_dates$death_not_scored) + 14,
             ymin = 0,
             ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "WIS rel. to baseline", x = "Date")

@@

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))] %>%
  c("coverage_deviation")
df[, (del_cols) := NULL]

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

@@

  p <- df[grepl(2, target)] %>%
    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
    geom_line() +
    geom_line(aes(y = true_value), color = "black") + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                            max(forecast_dates$full_hub_period))) + 
    labs(y = "Median forecast", x = "Date")
  return(p)
}

@@

```{r}
scores <- eval_forecasts(
  filtered_data[(model %in% regular_models) & grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
                   "target_phase",
                   "location_target", "classification"),
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

@@

# look at variance to check
scores[, .(sd = sd(scaled_rel_skill)), by = c("model")]

distribution_plot <- function(df, x = "scaled_rel_skill") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model")) + 
    geom_density_ridges(aes(fill = model), 
                                  quantile_lines = TRUE, quantiles = 0.5, 
                                  rel_min_height = 0.01) + 
    geom_vline(aes(xintercept = 1), alpha = 0.4) + 
    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Scaled relative skill") + 
    scale_x_log10(labels = scales::number_format(accuracy = 0.1))
}

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    geom_density_ridges(aes(fill = model), 
                        quantile_lines = TRUE, quantiles = 0.5, 
                        rel_min_height = 0.005, 
                        scale = 0.9, 
                        jittered_points = TRUE, 
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_size = 1.5, 
                        point_shape = 21,
                        #point_shape = '|',
                        point_alpha = 1, 
                        alpha = 0.7) + 
    geom_density_ridges(quantile_lines=TRUE,
                        quantile_fun=function(x,...) mean(x), 
                        linetype = "dotted", 
                        alpha = 0, 
                        scale = 0.9, 
                        rel_min_height = 0.01) +
    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL))
}

p_combined <- distribution_plot(df = scores[model != "Baseline"]) + 
  facet_wrap(~ target_type, ncol = 1)

p_combined_wis <- distribution_plot_wis(df = scores, 
                                        x = "interval_score") +
  facet_wrap(~ target_type, ncol = 1, scales = "free") + 
  theme(plot.margin=unit(c(0,0.4,0,0),"cm"))

@@

p <- distribution_plot(df = scores[model != "Baseline"]) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2)

p_wis <- distribution_plot_wis(df = scores) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free")

@@

```{r}
# scores for different phases of the epidemic
scores[, target_phase := factor(target_phase, 
                                levels = str_to_title(c("Cases - decreasing phase", 
                                                        "Cases - unclear phase", 
                                                        "Cases - increasing phase", 
                                                        "Deaths - decreasing phase", 
                                                        "Deaths - unclear phase", 
                                                        "Deaths - increasing phase")))]

scores[, .(target_count = .N), by = c("target_phase", "model")]

p_phases <- distribution_plot(df = scores[model != "Baseline"]) + 
  facet_wrap( ~ target_phase)

p_phases_wis <- distribution_plot_wis(df = scores) + 
  facet_wrap( ~ target_phase, scales = "free_x")

@@

pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

ggsave("plots/distribution_scores.png", plot = pl, height = 9)

ggsave("plots/distribution_scores_wis.png", pl_wis, height = 11, width = 9)

@@

```{r, eval = TRUE}
scores_full <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
  compute_relative_skill = FALSE, 
  baseline = "Baseline"
)

@@

scores_full %>%
  ggplot(aes(y = interval_score, x = horizon, 
             fill = model, color = model)) +
  geom_boxplot(outlier.shape = 21, coef = 1.5, 
               width=0.5, alpha = 1, 
               position = position_dodge2(width = 0.5)) + 
  # geom_line(data = means, 
  #           aes(group = model, y = meanval, color = model), 
  #           position = position_dodge2(width = 0.5), 
  #           size = 2) +
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_color_brewer(palette = "Accent") + 
  geom_point(data = means, 
             mapping = aes(y = meanval, fill = model),
             color = "black",
             # fill = "red",
             shape = 21,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
    geom_point(data = means, 
             mapping = aes(y = medianval, fill = model),
             color = "black",
             # fill = "red",
             shape = 22,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
  scale_fill_brewer(palette = "Accent") + 
  scale_y_log10() + 
  facet_wrap( ~ location_target, scales = "free") + 
  theme(legend.position = "bottom")

@@

```{r, eval = FALSE}
scores <- list()
# scores for restricted data set
scores_full <- eval_forecasts(filtered_data, 
                              summarise_by = c("model", "target_type", "target"), 
                              compute_relative_skill = TRUE, 
                              baseline = "Baseline")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)

# define colors for deaths and cases
colcases <- brewer.pal(name = "Accent", n = 5)[-c(1, 4)]
coldeaths <- brewer.pal(name = "Accent", n = 5)[-4]

@@

@@

```{r}
dailytruth_data %>%
  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
                target_end_date <= max(forecast_dates$full_hub_period)) %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_point(size = 0.3, alpha = 0.4) + 
  geom_line(size = 0.5, alpha = 0.4) + 
  geom_line(data = truth_data, aes(y = true_value / 7)) + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  labs(y = "Observed values", x = "Date") + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
                            max(forecast_dates$full_hub_period)))
  theme_light()

@@

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df) {
  p <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.7,
                 alpha = 1,
                 position = position_dodge(width = 4)) + 
    geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
                   size = 1.7,
                   alpha = 0.1,
                   position = position_dodge(width = 4)) +   
    geom_point(aes(shape = classification)) + 
  geom_line() + 
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom") + 
  # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

df <- unfiltered_data[model %in% regular_models &
                        quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
  dcast(... ~ quantile, value.var = "prediction")
df <- merge(
  df[, c("classification", "speed") := NULL], 
  copy(epitrend)[, forecast_date := NULL], 
  by = c("target_end_date", "location_name", "target_type")
)

@@

for (horizon in 1:4) {
  # plot for cases
  truth_vs_forecast_cases <- df[grepl(horizon, target)] %>%
    dplyr::filter(target_type == "case") %>%
    truth_and_pred_plot() + 
    scale_color_manual(values = colcases) + 
    labs(y = "Cases", x = "")

@@

  # plot for deaths
  truth_vs_forecast_deaths <- df[grepl(horizon, target)] %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_pred_plot()  + 
  scale_color_manual(values = coldeaths) + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "Deaths", x = "")

@@

# pairwise <- pairwise_comparison(scores_target_forecastdate, 
#                                 summarise_by = summarise_by, 
#                                 baseline = "Baseline")
# pairwise <- pairwise[compare_against == "Baseline"]

# create helper function to plot forecasts -------------------------------------
scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = 0,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  # scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

# create plots for all horizons ------------------------------------------------
for (i in 1:4) {
  scores_over_time_case <- scores_target_forecastdate[horizon == i & target_type == "case"] %>%
    scores_over_time_plot(y = "interval_score") + 
    scale_color_manual(values = colcases) + 
    labs(y = "WIS rel. to baseline", x = "")

@@

  scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
    scores_over_time_plot(y = "interval_score") + 
    scale_color_brewer(palette = "Accent") + 
    annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
             xmax = max(forecast_dates$death_not_scored) + 14,
             ymin = 0,
             ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "WIS rel. to baseline", x = "Date")

@@

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE,
  sd = TRUE, 
  quantiles = 0.5
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))] %>%
  c("coverage_deviation")
df[, (del_cols) := NULL]

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

@@

  p <- df[grepl(2, target)] %>%
    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
    geom_line() +
    geom_line(aes(y = true_value), color = "black") + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                            max(forecast_dates$full_hub_period))) + 
    labs(y = "Median forecast", x = "Date")
  return(p)
}

@@

```{r}
scores <- eval_forecasts(
  filtered_data[(model %in% regular_models)], 
  summarise_by = c("model", "target_type", "location_name", "horizon", 
                   "forecast_date", "target_phase",
                   "location_target", "classification"),
  compute_relative_skill = FALSE
)

@@

# scores for different phases of the epidemic
scores[, target_phase := factor(target_phase, 
                                levels = str_to_title(c("Cases - decreasing phase", 
                                                        "Cases - unclear phase", 
                                                        "Cases - increasing phase", 
                                                        "Deaths - decreasing phase", 
                                                        "Deaths - unclear phase", 
                                                        "Deaths - increasing phase")))]

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    # geom_density_ridges(aes(fill = model, color = NA),
    #                     rel_min_height = 0.005,
    #                     scale = 0.9,
    #                     # jittered_points = TRUE,
    #                     # position = position_points_jitter(width = 0.05, height = 0),
    #                     point_size = 1.5,
    #                     point_shape = 21,
    #                     #point_shape = '|',
    #                     point_alpha = 1,
    #                     alpha = 0.3) +
    ggdist::stat_dots(aes(color = model)) + 
    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
    # geom_density_ridges(quantile_lines=TRUE,
    #                     quantile_fun=function(x,...) mean(x), 
    #                     linetype = "dotted", 
    #                     alpha = 0, 
    #                     scale = 0.9, 
    #                     rel_min_height = 0.01) +
    scale_fill_manual(values = coldeaths) + 
    scale_color_manual(values = coldeaths) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL))
}

for (i in 1:4) {
  p_combined_wis <- distribution_plot_wis(df = scores[horizon == i], 
                                          x = "interval_score") +
    facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm"))

  p_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free")

  p_phases_wis <- distribution_plot_wis(df = scores[horizon == i]) + 
    facet_wrap( ~ target_phase, scales = "free_x")

  ggsave(here("analysis", "plots", 
              paste0("distribution_scores_wis-", i, ".png")), 
         pl_wis, height = 11, width = 9)

}

@@

# p <- distribution_plot(df = scores[model != "Baseline"]) + 
#   theme(axis.title.y=element_blank(),
#         axis.text.y=element_blank(), 
#         axis.ticks.y = element_blank()) + 
#   facet_wrap(~ location_target, ncol = 2)

@@

```{r}
scores[, .(target_count = .N), by = c("target_phase", "model")]

# p_phases <- distribution_plot(df = scores[model != "Baseline"]) + 
#   facet_wrap( ~ target_phase)

@@

# pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
#   plot_layout(guides = "collect") & 
#   plot_annotation(tag_levels = 'A') &
#   theme(legend.position = 'bottom') 
# 
# ggsave("plots/distribution_scores.png", plot = pl, height = 9)

@@

```{r, eval = TRUE}
scores_full <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
  compute_relative_skill = FALSE
)

@@

scores_full %>%
  ggplot(aes(y = interval_score, x = horizon, 
             fill = model, color = model)) +
  geom_boxplot(outlier.shape = 21, coef = 1.5, 
               width=0.5, alpha = 1, 
               position = position_dodge2(width = 0.5)) + 
  # geom_line(data = means, 
  #           aes(group = model, y = meanval, color = model), 
  #           position = position_dodge2(width = 0.5), 
  #           size = 2) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_color_brewer(palette = "Accent") + 
  geom_point(data = means, 
             mapping = aes(y = meanval, fill = model),
             color = "black",
             # fill = "red",
             shape = 21,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
    geom_point(data = means, 
             mapping = aes(y = medianval, fill = model),
             color = "black",
             # fill = "red",
             shape = 22,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
  scale_fill_brewer(palette = "Accent") + 
  scale_y_log10() + 
  facet_wrap( ~ location_target, scales = "free") + 
  theme(legend.position = "bottom")

@@

```{r, eval = FALSE}
scores <- list()
# scores for restricted data set
scores_full <- eval_forecasts(filtered_data, 
                              summarise_by = c("model", "target_type", "target"), 
                              compute_relative_skill = TRUE)

@@

``` {r}

scores <- eval_forecasts(filtered_data[model %in% regular_models], 
                         summarise_by = c("model", "target_type", "horizon"), 
                         quantiles = 0.5, 
                         sd = TRUE)

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))

# median performance
p_median <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-median.png"))

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))

# bias
p_bias <- scores %>%
  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))

# coverage
scores <- eval_forecasts(filtered_data[model %in% regular_models], 
                         summarise_by = c("model", "target_type", "horizon", "range"), 
                         quantiles = 0.5, 
                         sd = TRUE)

scores[range %in% c(50, 90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = range, color = range)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(model ~ target_type , scales = "free_y")

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.9, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))

p_combined <- (p_mean + p_median) / 
  (p_aem + p_wis_sd) / 
  (p_sharpness + p_bias) / 
  (p_cov50 + p_cov90) +  
    plot_layout(guides = "collect") & 
    plot_annotation(tag_levels = 'A') &
    theme(legend.position = 'bottom')

ggsave(here("analysis", "plots", "aggregate-performance-all.png"), 
       height = 12, width = 10)

## Plots with all forecasts

```{r}
# only select every second forecast date to stratify
df <- unfiltered_data[model %in% regular_models &
                        quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
  dcast(... ~ quantile, value.var = "prediction")
df <- merge(
  df[, c("classification", "speed") := NULL], 
  copy(epitrend)[, forecast_date := NULL], 
  by = c("target_end_date", "location_name", "target_type")
)

df[, forecast_date := as.Date(forecast_date)]
df[, i := as.numeric(forecast_date - as.Date(min(forecast_date))) %% 2 + 1]

plot_forecast <- function(df, m = "Renewal") {
  min_date <- min(forecast_dates$unfiltered)
  plot_dates <- c((min_date - c(28, 21, 14, 7)), forecast_dates$unfiltered)
  plot_dates <- plot_dates - 2
  d <- copy(truth_data)[, location_target := paste0(str_to_sentence(target_type), 
                                                    "s", " in ", location_name)]
  daily <- copy(dailytruth_data)[, location_target := paste0(str_to_sentence(target_type), 
                                                             "s", " in ", location_name)]
  daily[, week := as_yearweek(target_end_date, firstday = 7L)]
  daily[, sum_val := sum(true_value), by = c("week", "location_target")]
  daily[, scaled_val := true_value - sum_val / 7]

  df <- copy(df)[, forecast_date := as.factor(forecast_date)]

  df[model == m] %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_line() + 
    geom_line(data = d[target_end_date %in% plot_dates],
              aes(y = true_value, x = target_end_date)) +
    geom_line(data = daily[target_end_date >= min(plot_dates) & target_end_date <= max(plot_dates)],
              aes(y = scaled_val, x = target_end_date), alpha = 0.4) +
    geom_vline(aes(xintercept = as.Date(forecast_date), 
                   color = forecast_date), alpha = 0.3, size = 0.4) + 
    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.025`, ymax = `0.975`, 
                                      group = forecast_date, 
                                      fill = forecast_date), alpha = 0.3) +
    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.25`, ymax = `0.75`, 
                                      group = forecast_date, 
                                      fill = forecast_date), alpha = 0.5) +
    ggplot2::geom_line(aes(y = `0.5`,group = forecast_date, 
                           colour = forecast_date), alpha = 1) +
    geom_point() + 
    theme_light() + 
    facet_grid(location_target ~ i, scale = "free_y") + 
    theme(legend.position = "bottom") 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    # scale_y_log10() 
}

for (m in c("Renewal", "Convolution", "Crowd forecast")) {
  p <- plot_forecast(df[horizon <= 2], m = m)

  saveRDS(p, file = here("analysis", "plots", 
                         paste0("all-forecasts-", m,".RDS")))

  ggsave(here("analysis", "plots", 
                         paste0("all-forecasts-", m,".png")), 
         height = 15, width = 10)

}
